---
title: "Lux Models"
author: "S. Katie Fogg"
date: "April 16, 2018"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}

```

## Sunny Station Lux Model (Summer)

```{r, echo=F, message=FALSE, warning=FALSE, comment = ""}
library(plyr)
library(RODBC)
library(stringr)
library(lubridate)
library(zoo)
library(xts)

bcol <- c("red", "orange", "gold", "chartreuse3", "cyan3") 

meacham <- odbcConnect("meacham_heat")

ssunnywslux <- sqlQuery(meacham, "SELECT * 
                          FROM observations 
                          WHERE metricIDX IN 
                              (SELECT metricIDX FROM metrics WHERE metricName = 'Lux') 
                          AND deploymentIDX IN 
                              (SELECT deploymentIDX FROM deployments WHERE deploymentName LIKE 'SSunnyWSLux%')")
ssunnywspy <- sqlQuery(meacham, "SELECT * 
                          FROM observations 
                        WHERE metricIDX IN 
                        (SELECT metricIDX FROM metrics WHERE metricName = 'SolarRadiation') 
                        AND deploymentIDX IN 
                        (SELECT deploymentIDX FROM deployments WHERE deploymentName LIKE 'SSunnyWSPyranometerUp%')")

sunnyLuxSolRad <- join(data.frame(observationTime = ssunnywslux$observationTime, sunnyLux = ssunnywslux$value), 
                       data.frame(observationTime = ssunnywspy$observationTime, sunnySolRad = ssunnywspy$value), 
                       by = "observationTime", 
                       type= "inner")


# Linear model of solar radiation as a function of Lux
sunnyLuxCal <- lm(sunnySolRad ~ sunnyLux, data = sunnyLuxSolRad)

summary(sunnyLuxCal)

plot(sunnySolRad ~ sunnyLux, data = sunnyLuxSolRad, ylab = "Pyranometer (W/m2)", xlab = "Lux")
abline(sunnyLuxCal, col = "violet", lwd = 2)

plot(sunnyLuxSolRad$sunnySolRad, type = "l", ylab = "Pyranometer (W/m2)", xlab = "Time", ylim = c(0, 1500))
lines((sunnyLuxSolRad$sunnyLux * coef(sunnyLuxCal)[2]) + coef(sunnyLuxCal)[1], col = "blue")
legend("topleft", c("Pyranometer measurement", "Lux logger measurement"), col = c("black", "blue"), lty = 1, lwd = 1)
```


$\mathrm{kW/m^{2}}$ pyranometer: `r sum(sunnyLuxSolRad$sunnySolRad)`

$\mathrm{kW/m^{2}}$ lux logger: `r sum((sunnyLuxSolRad$sunnyLux * coef(sunnyLuxCal)[2]) + coef(sunnyLuxCal)[1])`

Difference in $\mathrm{kW/m^{2}}$ between the pyranometer measurement and the calibrated lux logger measurements over study time period: `r sum(sunnyLuxSolRad$sunnySolRad) - sum((sunnyLuxSolRad$sunnyLux * coef(sunnyLuxCal)[2]) + coef(sunnyLuxCal)[1])`

## Shady Station Lux Model (Summer)

```{r echo=F, message=FALSE, warning=FALSE, comment = ""}
sshadywslux <- sqlQuery(meacham, "SELECT * 
                          FROM observations 
                        WHERE metricIDX IN 
                        (SELECT metricIDX FROM metrics WHERE metricName = 'Lux') 
                        AND deploymentIDX IN 
                        (SELECT deploymentIDX FROM deployments WHERE deploymentName LIKE 'SShadyWSLux%')")
sshadywspy <- sqlQuery(meacham, "SELECT * 
                       FROM observations 
                       WHERE metricIDX IN 
                       (SELECT metricIDX FROM metrics WHERE metricName = 'SolarRadiation') 
                       AND deploymentIDX IN 
                       (SELECT deploymentIDX FROM deployments WHERE deploymentName LIKE 'SShadyWSPyranometerUp%')")

shadyLuxSolRad <- join(data.frame(observationTime = sshadywslux$observationTime, shadyLux = sshadywslux$value), 
                       data.frame(observationTime = sshadywspy$observationTime, shadySolRad = sshadywspy$value), 
                       by = "observationTime", 
                       type= "inner")
shadyLuxCal <- lm(shadySolRad ~ shadyLux, data = shadyLuxSolRad)
summary(shadyLuxCal)

plot(shadySolRad ~ shadyLux, data = shadyLuxSolRad, ylab = "Pyranometer (W/m2)", xlab = "Lux")
abline(shadyLuxCal, col = "violet", lwd = 2)

plot(shadyLuxSolRad$shadySolRad, type = "l", ylab = "Pyranometer (W/m2)", xlab = "Time", ylim = c(0, 1500))
lines((shadyLuxSolRad$shadyLux * coef(shadyLuxCal)[2]) + coef(shadyLuxCal)[1], col = "blue")
legend("topleft", c("Pyranometer measurement", "Lux logger measurement"), col = c("black", "blue"), lty = 1, lwd = 1)

sum(shadyLuxSolRad$shadySolRad) 
sum((shadyLuxSolRad$shadyLux * coef(shadyLuxCal)[2]) + coef(shadyLuxCal)[1])
sum(shadyLuxSolRad$shadySolRad) - sum((shadyLuxSolRad$shadyLux * coef(shadyLuxCal)[2]) + coef(shadyLuxCal)[1])

```

$\mathrm{kW/m^{2}}$ pyranometer: `r sum(shadyLuxSolRad$shadySolRad)`

$\mathrm{kW/m^{2}}$ lux logger: `r sum((shadyLuxSolRad$shadyLux * coef(shadyLuxCal)[1]))`

Difference in $\mathrm{kW/m^{2}}$ between the pyranometer measurement and the calibrated lux logger measurements over study time period: `r sum(shadyLuxSolRad$shadySolRad) - sum((shadyLuxSolRad$shadyLux * coef(shadyLuxCal)[1]))`

## Summer Combined Model

```{r echo=F, message=FALSE, warning=FALSE, comment = ""}
summerLuxSolRad <- join(sunnyLuxSolRad, shadyLuxSolRad, by = "observationTime", type= "inner")

summerLuxSolRadLong <- data.frame(observationTime = rep(summerLuxSolRad$observationTime, times = 2),
                                  lux = c(summerLuxSolRad$sunnyLux, summerLuxSolRad$shadyLux),
                                  solRad = c(summerLuxSolRad$sunnySolRad, summerLuxSolRad$shadySolRad),
                                  site = factor(c(rep("sunny", times = length(summerLuxSolRad$observationTime)), 
                                                  rep("shady", times = length(summerLuxSolRad$observationTime)))))
summerCal <- lm(solRad ~ lux * site, data = summerLuxSolRadLong)
summary(summerCal)


summerCal2 <- lm(solRad ~ lux, data = summerLuxSolRadLong)
summary(summerCal2)


plot(solRad ~ lux, data = subset(summerLuxSolRadLong, summerLuxSolRadLong$site == "sunny"))
points(solRad ~ lux, data = subset(summerLuxSolRadLong, summerLuxSolRadLong$site == "shady"), col ="gray")
abline(summerCal, col = "gray", lwd = 2)
abline(coef(summerCal)[1] + coef(summerCal)[3], coef(summerCal)[2] + coef(summerCal)[4], lwd=2)




plot(subset(summerLuxSolRadLong, site == "sunny")$solRad, type = "l")
lines(subset(summerLuxSolRadLong, site == "shady")$solRad, col = "gray50")
lines((subset(summerLuxSolRadLong, site == "sunny")$lux * coef(summerCal2)[2]) + coef(summerCal2)[1], col = "blue")
lines((subset(summerLuxSolRadLong, site == "shady")$lux * coef(summerCal2)[2]) + coef(summerCal2)[1], col = "steelblue")

sum(subset(summerLuxSolRadLong, site == "sunny")$solRad)
sum((subset(summerLuxSolRadLong, site == "sunny")$lux * coef(summerCal2)[2]) + coef(summerCal2)[1])
sum(subset(summerLuxSolRadLong, site == "sunny")$solRad) - sum((subset(summerLuxSolRadLong, site == "sunny")$lux * coef(summerCal2)[2]) + coef(summerCal2)[1])

sum(subset(summerLuxSolRadLong, site == "shady")$solRad)
sum((subset(summerLuxSolRadLong, site == "shady")$lux * coef(summerCal2)[2]) + coef(summerCal2)[1])
sum(subset(summerLuxSolRadLong, site == "shady")$solRad) - sum((subset(summerLuxSolRadLong, site == "shady")$lux * coef(summerCal2)[2]) + coef(summerCal2)[1])
```


Calibration might be specific to a particular lux logger. Calibrate all lux loggers against the pyranometers???
